---
title: Work Health and Safety
output: 
  html_document:
    theme: lumen           
    highlight: tango
    css: styles.css
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo          = FALSE, 
                      warning       = FALSE, 
                      message       = FALSE, 
                      warning       = FALSE, 
                      fig.fullwidth = TRUE, 
                      paged.print   = FALSE, 
                      comment       = NA)

```



## {.tabset .tabset-fade}

### Index analysis

\

The following analysis is based on work health and safety questions in the LG21 staff survey, using only complete responses 
(`r format(complete_responses, big.mark=",")`). The original survey response data have been  transformed, so every
staff response is assigned an index score between 1 (most negative responses) and 5 (most positive responses). Only selected questions contributed to the index for each topic. See the 'Analysis - Index questions' page for a list of questions used in each index and a description of how to read the box plots.

The boxplots below (Fig A) show index scores for work health and safety questions for each respondent compared to other index topics (left) and the work health and safety index scores for respondents broken down by role (right).

Overall, responses to work health and safety questions were more positive than for all other topics. Across roles, EO's tended to provide more negative feedback than staff in other roles. 

\

#### **Fig A). Survey responses, aggregated by all topics (left), and by role for work health and safety questions (right. Note ROs were excluded from the index analysis)**

```{r fig.align = "center", fig.width = 15, fig.height = 7}

## Arrange a grid
plot_grid(bp_resposes_all, 
          respondent_role_boxplots[["WHS_boxplot"]],
          nrow = 1,
          label_size = 5, align = 'hv')


```

\



### Index Map

\


#### **Fig C). Work health and safety survey responses by RO Region**

The map below shows the index of survey responses for work health and safety questions in the LG21 staff survey. The underlying data are the same index
values used in the boxplots, but are the average of all the staff responses within each RO Region (the blue boundaries on the map). The blank regions are non-client or uncontested Councils (Central Coast, Fairfield, Penrith, Wingecarribee), unincorporated areas of NSW and the ACT.

```{r fig.align = "center", fig.width = 10, fig.height = 10}


RO_region_polygon_index_maps[["WHS_polygon_map"]]


```

