---
title: Index questions
output: 
  html_document:
    theme: lumen           
    highlight: tango
    css: styles.css
---

<style type="text/css">

.main-container {
max-width: 1400px;
margin-left: 180px;
margin-right: auto;

}

</style>


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo          = FALSE, 
                      warning       = FALSE, 
                      message       = FALSE, 
                      warning       = FALSE, 
                      fig.fullwidth = TRUE, 
                      paged.print   = FALSE, 
                      comment       = NA)

```


## {.tabset .tabset-fade}

### Index questions


<!-- Set alignment property for the following container -->
<div align="left">

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA}

datatable(LUT_index
          # Set width of table in container, requires fillContainer to be set to FALSE
          ,width = '95%'
          ,fillContainer = FALSE
          
          ,rownames   = FALSE
          ,extensions = 'Buttons'
          ,filter     = 'top'
          ,caption    = 'Table of Questions for Survey Index'
          
          ,options = list(
            pageLength = 100
            ,dom = 'tip'
            ,scrollY = TRUE
            
            # Control individual column width (requires autoWidth to be set to TRUE)
            # targets argument refers to column postitions which are zero indexed
            ,autoWidth = TRUE
            ,columnDefs = list(list(width  = '150px', targets = c(0))
                               ,list(width = '50px', targets = c(1, 3))
            )))

```
</div>



### Index Calculation


\

In the formatted staff survey data table, rows are people (i.e. 'respondents', n=10899), and the columns  
are questions (n = 382, indcluding all sub-questions). To analyse the survery results numerically, the original   
survey responses have been transformed, so every staff response (i.e. row) is assgined a numerical, ordinal   
value representing postive or negative responses (i.e. a whole number from high to low). For example, for   
the five-scale satisfaction questions, transformed numerical values are as follows:  

\

**Very satisfactory   ~ 5**  
**Satisfactory        ~ 4**  
**Neutral             ~ 3**  
**Unsatisfactory      ~ 2**  
**Very unsatisfactory ~ 1**      

\

For the questions in other formats (e.g. yes/no/uncertain), we use two different transformations -  
one where yes is positive, and one where no is positive (depending on the context of the question):  

\

**Yes       ~ 3 (or 1)**  
**Uncertain ~ 2 (2)**  
**No        ~ 1 (or 3)**  

\

Using these numeric values, the overall index for each topic is calculated as the sum of all questions  
in that theme for each respondent (i.e. row), divided by the maximum possible score for each topic -  
but only for those people who answered each question in that topic. For example, the Staffing Index has   
four questions, two yes/no questions, and two satisfaction questions, with a maximum score of 16. If   
a particular respondent only answered the two satisfaction staffing questions, their individual staffing   
score would only be divided by the max score of 10 (2*5). However, the score of a respondent who answered  
all staffing questions would be divied by the maximum of 16.    

\

These respondent-level indexes give a better indication of the variation in survey responses across the  
whole survey, rather than aggregating the index scores to some arbitary unit (for example the spatial unit  
of Venue or the RO Office where each staff member worked). The boxplots below show the variation in the index  
scores for each topic across all responents, using the standard format of the five-number summary (**Fig A**).  
The minimum and maximum values are shown by the whiskers, the first quartile (Q1) is the lower half of each  
coloured box, the median value (centre of the distribution) is the solid black line, and the third quartile  
(Q3) is the upper half of the coloured box. For example, Index values for the IS topic varied more than for  
the Training or WHS Topics, due to the nature of the questions chosen for each Topic's index. To further  
illustrate the point, the variation in each index is also given in table form below the boxplot.    

\

```{r fig.align = "left", fig.width = 10, fig.height = 7}

bp_resposes_all

```
**Fig A).** Boxplots of individual Survey Responses for each Topic**

\


