---
title: Staffing
output: 
  html_document:
    theme: lumen           
    highlight: tango
    css: styles.css
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo          = FALSE, 
                      warning       = FALSE, 
                      message       = FALSE, 
                      warning       = FALSE, 
                      fig.fullwidth = TRUE, 
                      paged.print   = FALSE, 
                      comment       = NA)

```



## {.tabset .tabset-fade}

### Index analysis

\

The following analysis is based on staffing questions in the LG21 staff survey, using only complete responses 
(`r format(complete_responses, big.mark=",")`). The original survey response data have been  transformed, so every
staff response is assigned an index score between 1 (most negative responses) and 5 (most positive responses). Only selected questions contributed to the index for each topic. See the 'Analysis - Index questions' page for a list of questions used in each index and a description of how to read the box plots.

The boxplots below (Fig A) show index scores for staffing questions for each respondent compared to other index topics (left) and the staffing index scores for respondents broken down by role (right).

Overall, responses to staffing questions were similar to most other topics. Across roles, SOAPP's tended to provide slightly more negative feedback than staff in other roles. 

\

#### **Fig A). Survey responses, aggregated by all topics (left), and by role for staffing (right)**

```{r fig.align = "center", fig.width = 15, fig.height = 7}

## Arrange a grid
plot_grid(bp_resposes_all, 
          respondent_role_boxplots[["Staffing_boxplot"]],
          nrow = 1,
          label_size = 5, align = 'hv')

```


\

Index scores were also broken down by staff demographics and whether they are located in a metropolitan or regional area (Fig B). The analysis below suggests that there were no differences in response to staffing questions across the demographic categories (left). People from remote areas tended to provide slightly more positive staffing feedback (right).

\

#### **Fig B). Survey responses by demographics and remoteness for staffing (note, categories are not necessarily mutually exclusive)**

```{r fig.align = "center", fig.width = 15, fig.height = 7}

## Arrange a grid
plot_grid(respondent_demo_boxplots[["Staffing_boxplot"]], 
          respondent_remoteness_boxplots[["Staffing_boxplot"]],
          nrow = 1,
          label_size = 5, align = 'hv')


```

\


### Index Map

\

#### **Fig C). Recruitment survey responses by RO Region**

The map below shows the index of survey responses for staffing questions in the LG21 staff survey. The underlying data are the same index
values used in the boxplots, but are the average of all the staff responses within each RO Region (the blue boundaries on the map). The blank regions are non-client or uncontested Councils (Central Coast, Fairfield, Penrith, Wingecarribee), unincorporated areas of NSW and the ACT.

```{r fig.align = "center", fig.width = 10, fig.height = 10}

RO_region_polygon_index_maps[["Staffing_polygon_map"]]

```


