---
title: Executive Summary
output:
  html_document:
    toc: true               # Table of content true
    toc_depth: 4            # Up to three depths of headings (specified by #, ## and html_document
    toc_float: true
    number_sections: false  # If you want number sections at each table header
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo          = FALSE, 
                      warning       = FALSE, 
                      message       = FALSE, 
                      warning       = FALSE, 
                      fig.fullwidth = TRUE, 
                      paged.print   = FALSE, 
                      comment       = NA)

```


The analysis in this report is based on the results of the Election Staff Survey, following the Local Government 
Election held on 4th December, 2021. The results use only complete survey responses.  


\

# **Response rate** 
The survey was emailed to around 29 thousand temporary election staff members between 15/12/2021 and 22/12/2021. 
The overall response rate was approximately `r all_resp_rate` per cent, with `r format(complete_responses, big.mark=",")` completed surveys (a completed survey response rate of `r complete_resp_rate` per cent). The highest response rate was from PPM's (over 50 per cent) and lowest for OA's (less than 20 per cent; see Table 1).   

\

<!-- Set alignment property for the following container -->
<div align="left">

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA}

datatable(response_rate_role %>% 
            arrange(desc(ResponseRate)) %>%
            rename(`ResponseRate_%` = ResponseRate)
                      
          # Set width of table in container, requires fillContainer to be set to FALSE
          ,width = '95%'
          ,fillContainer = FALSE
          
          ,rownames   = FALSE
          ,extensions = 'Buttons'
          ,filter     = 'none'
          ,caption    = 'Table 1: Response rates by role for the LG21 Staff Survey'
          
          ,options = list(
            pageLength = 100
            ,dom = 't'
            ,scrollY = TRUE
            
            # Control individual column width (requires autoWidth to be set to TRUE)
            # targets argument refers to column postitions which are zero indexed
            ,autoWidth = TRUE
            ,columnDefs = list(list(width = '150px', targets = c(0))
                               ,list(width = '50px', targets = c(1, 3))
            )))

```
</div>
\

# **Work health safety guidelines** 
The NSWEC implemented a new suite of WHS guidelines at this election, and the results show that most staff   
reported compliance with the measures. Figure 1 shows that the vast majority of staff stated they finished   
work before the mandated 11pm cut-off on election night. Although 12 per cent of respondents had some WHS   
concerns (Q169), overall, the WHS and COVID-safe measures were well received. Ninety five per cent of   
respondents were satisfied with the COVID-safe measures (Q2).

\

```{r fig.align = "center", fig.width=20, fig.height=10}

plot_grid(time_histograms[['L10_graph']], 
          nrow        = 1, 
          label_size  = 12, 
          align       = 'hv')

```

**Figure 1.** Number of staff finishing work at different times on Election Day. Each grey bar represents the number of staff 
finishing at a given time. The red line is the overall median finishing time (the middle value of all the finishing times). This plot shows that the vast 
majority of staff completed work prior to 11pm on election night.

\

# **Employee sentiment** 
Election staff overwhelmingly believed the election was run fairly (98%), and would work for the NSWEC at 
a future election (94%; Figure 2).        

\

```{r fig.align = "center", fig.width=20, fig.height=15}

grid.arrange(plots_yesno[["A1_graph"]],
             plots_yesno[["N4_graph"]], nrow = 2)

```
**Figure 2.** Bar charts of overall elector sentiment. 

\

```{r fig.width = 10, fig.height = 8, fig.align='center'}

Count <- BaseCount %>%
  filter(QuestionNumber == "N4b") %>% 
  .$BaseSize

if (Count >= 3) {
  
  Role <- role_list$N4b_Roles
  
  Role_caption <- paste(c(Role, Count, ' Responses'), collapse = " ") %>% str_wrap(50)
  
  layout(matrix(c(1, 2), nrow = 2), heights = c(1, 4))
  par(mar = rep(0, 4))
  plot.new()
  text(x = 0.5, y = 0.5, str_wrap(label_list[['N4b']], 40), cex = 2, font = 2)
  
  SurveyWordCloud(Survey_data$N4b, c("election", "elections"))
  
  text(x = 0.5, y = 0, Role_caption, cex = 1.5, font = 3)
  
} else {
  print("No data for this question")
}

```
**Figure 3.** Word cloud of staff sentiment regarding working at the elections again. 


```{r fig.width = 10, fig.height = 8, fig.align='center'}

Count <- BaseCount %>%
  filter(QuestionNumber == "N4a") %>% 
  .$BaseSize

if (Count >= 3) {
  
  Role <- role_list$N4a_Roles
  
  Role_caption <- paste(c(Role, Count, ' Responses'), collapse = " ") %>% str_wrap(50)
  
  layout(matrix(c(1, 2), nrow = 2), heights = c(1, 4))
  par(mar = rep(0, 4))
  plot.new()
  text(x = 0.5, y = 0.5, str_wrap(label_list[['N4a']], 40), cex = 2, font = 2)
  
  SurveyWordCloud(Survey_data$N4a, c("election", "elections"))
  
  text(x = 0.5, y = 0, Role_caption, cex = 1.5, font = 3)
  
} else {
  print("No data for this question")
}

```
**Figure 4.** Word cloud of staff sentiment regarding not working at the elections again. 

\

# **Overall employee satisfaction** 
Election staff were generally satisfied with how the election was run, with most questions across all topics having 
satisfaction ratings greater than 80 per cent, and dissatisfaction ratings less than 10 per cent (see Table of Contents: All satisfaction responses; 
Figure 5).        

\

```{r fig.align = "center", fig.width=20, fig.height=18}

Overall_satisfaction_graph

```


**Figure 5.** Bar-chart of combined satisfaction responses to survey questions across topics. Only 'satisfaction' type questions are included in this plot, and the RO/RO Office topic was only answered by **three respondents**.

\

# **Data use**


The results of the LG2101 staff survey can be used to support the continuous improvement of NSWEC election processes. When using the survey 
results, please feel free to consult with the Data Analytics and Geospatial Services team for help with interpretation and analysis.      

\
