---
title: "LG21 :: Demographic Survey Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    css: styles_LG_survey_font.css
---



```{r setup, include = FALSE}

knitr::opts_chunk$set(echo          = FALSE, 
                      warning       = FALSE, 
                      message       = FALSE, 
                      warning       = FALSE, 
                      fig.fullwidth = TRUE, 
                      paged.print   = FALSE, 
                      comment       = NA)

```



Demography Plots
=====================================

Column {data-width = 1}
-----------------------------------------------------------------------


Column {data-width = 12}
-----------------------------------------------------------------------

\

The following demohgraphic analysis is based on Voting questions in the LG21 staff survey,    
using only complete responses (n = 1356). These demographic analyses can be used to benchmark    
future Election Staff surveys. In the formatted staff survey data table, rows are people   
(n = 1356), and the columns are questions (n = 382). The original data has been transformed,   
so every staff response (i.e. row) is assgined an Index score between -1 (negative responses)   
and 1 (positive responses).  

\

The variable 'District Workload' is the TotalVotes / Total_projections for each district (**Fig A**).   
Figure A). Shows how the district workload is distributed across districts in different remoteness   
categories. The District workload is an indirect approximation for the stress the staff working at   
each venue would have been under.   

\

```{r fig.align = "center", fig.width=12, fig.height=5}

dist.votes.plot

```     

\

**Fig A).** Histograms of the difference between projected and total votes at the district level.    
The remotess categories are taken from the ABS : https://www.abs.gov.au/websitedbs/d3310114.nsf/home/remoteness+structure.    

\


The numerical indexes for each topic have been aggregated into a series of scatterplots. 
These plots show the indexes for each business topic at the district level, in relation 
to each other, and also in relation to the voting workload. The values in the top half of the 
scatterplot matrices (**Fig B**) represent the correlation coefficents - these are measures of 
the strength of the relationships between variables, ranging from -1 (strong negative relationship) 
to +1 (strong positive). To read the scatterplot matrix, look down the columm to a particular 
scatterplot for the x-variable, (EG "Informal" for Informal rate) then across the row for the 
y-variable (EG "High SES" for high socioeconomic status). For example, wealthier metro districts 
had lower informal voting rates, and vice versa. Similarly, the district-level workload has 
a negative corrleation with the informal voting rate in each district: districts with higher 
workloads tended to have lower informal voting rates. These relationships were stronger
for Districts in the major cities of Australia, than for Inner Regional or Outer Regional
Districts. However, the strength of these relationships were similar across CALD or Non-CALD 
districts (**Fig C**).

\

```{r fig.align = "center", fig.width=12, fig.height=10}

venue_work_ses_remotess_plot

```      

\

**Fig B).** Scatterplot of district-level workload for LG21 vs. informal votes and Socieoecomic status, by ABS remoteness category.   

\

<!-- ```{r fig.align = "center", fig.width=12, fig.height=10} -->

<!-- venue_work_ses_ -->

<!-- ```       -->

<!-- \ -->

<!-- **Fig c).** Scatterplot of district-level workload for LG21 vs. informal votes and Socieoecomic status, by ABS CALD category.     -->

<!-- \ -->

```{r fig.align = "center", fig.width=12, fig.height=10}

venue_work_ses_remotess_WHS_plot

```      

\

**Fig D).** Scatterplot of district-level WHS index for LG21 vs. Socieoecomic status, by ABS remoteness category.    

\

Column {data-width = 1}
-----------------------------------------------------------------------

\

Column {data-width = 1}
-----------------------------------------------------------------------


Demography Maps
=====================================

\

Column {data-width = 1}
-----------------------------------------------------------------------


Column {data-width = 12}
-----------------------------------------------------------------------

### **Fig D). District Satisfaction and CALD **
The map below shows the % CALD for each district, in relation to satisfaction responses for the LG21 staff survey.
\
```{r comment = NA, fig.width = 20, fig.height = 10}

# returning_CALD_choropleth

```

\

### **Fig E). District Satisfaction and ATSI **
The map below shows the % ATSI for each district, in relation to satisfaction responses for the LG21 staff survey.
\
```{r comment = NA, fig.width = 20, fig.height = 10}

# returning_ATSI_choropleth

```



Column {data-width = 1}
-----------------------------------------------------------------------


