---
title: "Business Unit Index Scatterplots"
output:
  html_document:
    toc: false
    toc_float: false
    css: styles_SG19_survey_sub_pages.css
---



```{r setup, include = FALSE}

knitr::opts_chunk$set(echo          = FALSE, 
                      warning       = FALSE, 
                      message       = FALSE, 
                      warning       = FALSE, 
                      fig.fullwidth = TRUE, 
                      paged.print   = FALSE, 
                      comment       = NA)

```


\
\

# **SOA venue-level response indices vs. workload (1679 SOAs)**
```{r venufig.align = "center", fig.width=25, fig.height=5}

scatterplot_venue_indexes_workload[["venue_SOA_load_plot_df"]]

```

\
\

# **SOAP venue-level response indices vs. workload (2419 SOAPs)**
```{r venufig.align = "center", fig.width=25, fig.height=5}

scatterplot_venue_indexes_workload[["venue_SOAP_load_plot_df"]]

```

\
\

# **EO venue-level response indices vs. workload (9450 EOs)**
```{r venufig.align = "center", fig.width=25, fig.height=8}

scatterplot_venue_indexes_workload[["venue_EO_load_plot_df"]]

```

\
\

# **District-level response indices vs. workload (93 Districts)**
```{r venufig.align = "center", fig.width=25, fig.height=5}

scatterplot_venue_indexes_workload[["venue_OA_load_plot_df"]]

```

\
\


# **District-level response indices vs. High SES (93 Districts)**
```{r venufig.align = "center", fig.width=25, fig.height=5}

scatterplot_venue_indexes_context_HSES[["venue_context_plot_df"]]

```

\
\


# **District-level response indices vs. Low SES(93 Districts)**
```{r venufig.align = "center", fig.width=25, fig.height=5}

scatterplot_venue_indexes_context_LSES[["venue_context_plot_df"]]

```

\
\


# **District-level response indices vs. Low SES(93 Districts)**
```{r venufig.align = "center", fig.width=25, fig.height=5}

scatterplot_venue_indexes_context_CALD[["venue_context_plot_df"]]

```

\
\

# **Venue-level response index correlations (all 2265 Venues)**
```{r venufig.align = "center", fig.width=25, fig.height=23}

venue_index_correlations_remote

```

\
\

# **RO-level response index correlations (all 93 Districts)**
```{r venufig.align = "center", fig.width=25, fig.height=23}

returning_index_correlations_remote

```

\
\
