---
title: "WHS Questions analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    css: styles_SG19_survey_font.css
---



Index analysis
=====================================

Column {data-width = 1}
-----------------------------------------------------------------------

Column {data-width = 20}
-----------------------------------------------------------------------

\

The following analysis is based on WHS questions in the SG19 staff survey,
using only complete responses (n = 1356). The original data has been transformed,
so every staff response (i.e. row) is assgined an Index score between -1 (negative 
response) and 1 (positive responses). The graphs below show the Index scores for 
questions realting to WHS for each Venue/District (Fig A). Overall, WHS 
questions scored lower than all other topics - statistical analysis shows that the 
WHIS Index scores are significantly lower (Fig A). 

\

Within the WHS scores, Election Managers gave overall postive responses, while EOs, 
SOAs and VCMs all repsonded negatively, with SOAs giving the strongest negative responses.
Statistical analysis showed that the differences between the WHS Index scores for each 
role are significant (), suggesting that (). Then we can break the WHS Index scores 
down by staff demographics, and the geographical remoteness of the Venue/District where 
staff worked (Fig B). WHS Index scores did not differ by demographics (), indicating the 
background of SG19 Election Staff did not affect their survey responses (?). Similary, 
the WHS scores did not differ by geographical remoteness ().

\


### **Fig A). SG19 Survey Responses, aggregated by District across all Topics(left), and by Role for WHS (right)**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 15, fig.height = 6}

## Arrange a grid
plot_grid(boxplots_indexes[["bp_district_all"]], 
          boxplots_role_indexes[["bp_district_Role_WHS"]],
          nrow = 1,
          label_size = 5, align = 'hv')

```


\

### **Fig B). WHS Survey Responses by Demoghraphic (categories are not necessarily mutually exclusive)**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 15, fig.height = 8}

## Arrange a grid
boxplots_combined_facetted_indexes[["bp_district_demography_WHS"]]

```

\


### **Fig C). WHS Survey Responses by geographic remoteness**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 8, fig.height = 5}

## Arrange a grid
boxplots_topic_remoteness_indexes[["WHS"]]

```

\


Column {data-width = 1}
-----------------------------------------------------------------------




Index Map
=====================================

\

Column {data-width = 1}
-----------------------------------------------------------------------


Column {data-width = 12}
-----------------------------------------------------------------------

### **Fig B). WHS Survey Responses by District**

</br> The map below shows the index of survey reponses for questions relating to WHS for the SG19 Staff Survey.
</br> See table of contents for details of how the Index was calculated.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA, fig.align = "center", fig.width = 20, fig.height = 10}

# latticeView(district_satisfaction_choropleth, 
#             district_dissatisfaction_choropleth,
#             
#             ncol = 2,  sync = "none", sync.cursor = FALSE,
#             no.initial.sync = TRUE)

district_WHS_choropleth


```


Column {data-width = 1}
-----------------------------------------------------------------------


<!-- Sentiment Analysis -->
<!-- ===================================== -->


<!-- Column {data-width = 1} -->
<!-- ----------------------------------------------------------------------- -->


<!-- Column {data-width = 12} -->
<!-- ----------------------------------------------------------------------- -->


<!-- Column {data-width = 1} -->
<!-- ----------------------------------------------------------------------- -->



