---
title: "Voting Operations Questions analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    css: styles_SG19_survey_font.css
---



Index analysis
=====================================

Column {data-width = 1}
-----------------------------------------------------------------------

Column {data-width = 12}
-----------------------------------------------------------------------

\

The following analysis is based on Voting Operations questions in the SG19 staff survey,
using only complete responses (n = 1356). The original data has been transformed,
so every staff response (i.e. row) is assgined an Index score between -1 (negative 
responses) and 1 (positive responses). The graphs below show that Index scores for 
questions relating to Voting Operations for each Venue/District (Fig A). Overall, 
Voting Operations questions scored similarly to other topics - statistical analysis 
shows that the Voting Operations Index scores are not significantly different to other 
topics (Fig A). 

\

Within the Voting Operations scores, all Roles gave mainly positive feedback, while 
Statistical analysis showed that the differences between the Voting Operations Index 
scores for each role are not significant (). Then we can break the IT Index scores 
down by staff demographics, and the geographical remoteness of the Venue/District 
where staff worked (Fig B). Voting Operations Index scores did not differ by demographics 
(), indicating the background of SG19 Election Staff did not affect their survey responses 
(?). Similary, the Voting Operations Index scores did not differ by geographical remoteness ().


\


### **Fig A). SG19 Survey Responses, aggregated by District across all Topics(left), and by Role for Voting Operations (right)**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 15, fig.height = 6}

## Arrange a grid
plot_grid(boxplots_indexes[["bp_district_all"]], 
          boxplots_role_indexes[["bp_district_Role_Operations"]],
          nrow = 1,
          label_size = 5, align = 'hv')

```


\

### **Fig B). Voting Operations Survey Responses by Demoghraphics (note, categories are not necessarily mutually exclusive)**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 15, fig.height = 8}

## Arrange a grid
boxplots_combined_facetted_indexes[["bp_district_demography_Operations"]]

```

\

### **Fig C). Voting Operations Survey Responses by geographic remoteness**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 8, fig.height = 5}

## Arrange a grid
boxplots_topic_remoteness_indexes[["Operations"]]

```

\



Column {data-width = 1}
-----------------------------------------------------------------------




Index Map
=====================================

\

Column {data-width = 1}
-----------------------------------------------------------------------


Column {data-width = 12}
-----------------------------------------------------------------------

### **Fig B). Voting Operations Survey Responses by District**

</br> The map below shows the index of survey reponses for questions relating to Voting Operations for the SG19 Staff Survey.
</br> See table of contents for details of how the Index was calculated.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA, fig.align = "center", fig.width = 20, fig.height = 10}

# latticeView(district_satisfaction_choropleth, 
#             district_dissatisfaction_choropleth,
#             
#             ncol = 2,  sync = "none", sync.cursor = FALSE,
#             no.initial.sync = TRUE)

district_Operations_choropleth


```


Column {data-width = 1}
-----------------------------------------------------------------------


<!-- Sentiment Analysis -->
<!-- ===================================== -->


<!-- Column {data-width = 1} -->
<!-- ----------------------------------------------------------------------- -->


<!-- Column {data-width = 12} -->
<!-- ----------------------------------------------------------------------- -->


<!-- Column {data-width = 1} -->
<!-- ----------------------------------------------------------------------- -->




