---
title: "Demography analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    css: styles_SG19_survey_font.css
---



Summary
=====================================

Column {data-width = 1}
-----------------------------------------------------------------------


Column {data-width = 12}
-----------------------------------------------------------------------


\

The following demohgraphic analysis is based on Voting questions in the SG19 staff survey,  
using only complete responses (n = 1356). These demographic analyses can be used to benchmark  
future Election Staff surveys.  


\


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}

## Arrange a grid
plot_grid(boxplots_indexes[["bp_district_all"]], 
          boxplots_indexes[["bp_venue_all"]],
          nrow = 1,
          label_size = 8, align = 'hv')

```
**Fig A).** Boxplots of Index values for Voting questions by Staff Role, and Role * Gender 

\

Column {data-width = 1}
-----------------------------------------------------------------------


Demography Maps
=====================================

\

Column {data-width = 1}
-----------------------------------------------------------------------


Column {data-width = 12}
-----------------------------------------------------------------------

### Survey Satisfaction by District
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA, fig.width = 20, fig.height = 10}

# latticeView(district_satisfaction_choropleth, 
#             district_dissatisfaction_choropleth,
#             
#             ncol = 2,  sync = "none", sync.cursor = FALSE,
#             no.initial.sync = TRUE)

district_CALD_choropleth


```

<!-- \ -->

### Survey Satisfaction by District
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA, fig.width = 20, fig.height = 10}


district_ATSI_choropleth


```



Column {data-width = 1}
-----------------------------------------------------------------------


Index analysis
=====================================

Column {data-width = 1}
-----------------------------------------------------------------------

Column {data-width = 12}
-----------------------------------------------------------------------

\

The Charts below show the Index values for questions realting to Voting, broken down by 
Election Staff Role and Demographic. First we have the index Voting Index Values for each 
Role (Fig A).

\


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 12, fig.height = 6}

## Arrange a grid
plot_grid(boxplots_indexes[["bp_district_all"]], 
          boxplots_indexes[["bp_venue_all"]],
          nrow = 1,
          label_size = 8, align = 'hv')

```
**Fig A).** Boxplots of Index values for Voting questions by Staff Role, and Role * Gender 

\

Then we have the Voting Index Values for each Role * CALD and Language (Fig B).

\


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 12, fig.height = 6}

## Arrange a grid
plot_grid(boxplots_indexes[["bp_em_all"]], 
          boxplots_indexes[["bp_soa_all"]], 
          nrow = 1,
          label_size = 8, align = 'hv')

```
**Fig B).** Boxplots of Index values for Voting questions by Staff Role *  CALD and Language

\

Then we have the Voting Index Values for each Role * Disability and Indigenous status (Fig C).

\


Column {data-width = 2}
-----------------------------------------------------------------------


Demography Plots
=====================================

Column {data-width = 1}
-----------------------------------------------------------------------


Column {data-width = 12}
-----------------------------------------------------------------------

\

The indexes have been aggregated into a series of scatterplot matrices. These 
plot the indexes for each business topic at the district level in relation to 
each other, and also in relation to the voting workload. The variable 'District Workload'   
is the TotalVotes / Total_projections for each district (**Fig A**). 
Both variables are proxies for the stress each staff member would be under. 

\

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA, fig.align = "center", fig.width=10, fig.height=3.5}

dist.votes.plot

```     
**Fig A).** Histograms of the difference between projected and total votes at the district level.    
The remotess categories are taken from the ABS : https://www.abs.gov.au/websitedbs/d3310114.nsf/home/remoteness+structure.    

\


The values in the top half of the matrix (**Fig B**) represent the correlation coefficents 
- these are measures of the strength of the relationships between variables, 
ranging from -1 (strong negative relationship) to +1 (strong positive). To read 
the scatterplot matrix, look down the columm to a particular scatterplot for the x-variable, 
(EG "Informal" for Informal rate) then across the row for the y-variable (EG High/Low SES). 
EG wealthier metro districts had lower informal voting rates, and vice versa. Similarly the 
district-level workload has a negative corrleation with the informal voting rate 
in each district: districts with higher workloads tended to have lower informal voting rates. 

\

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA, fig.align = "center", fig.width=14, fig.height=10}

district_work_ses_remotess_plot

```      
**Fig B).** Scatterplot of district-level workload for SG19 vs. informal votes and Socieoecomic status, by ABS remoteness category.   

\

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA, fig.align = "center", fig.width=14, fig.height=10}

district_work_ses_CALD_plot

```      
**Fig c).** Scatterplot of district-level workload for SG19 vs. informal votes and Socieoecomic status, by ABS CALD category.    

\


Column {data-width = 1}
-----------------------------------------------------------------------

