---
title: "Office Operations Questions analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    css: styles_SG19_survey_font.css
---



Index analysis
=====================================

Column {data-width = 1}
-----------------------------------------------------------------------

Column {data-width = 12}
-----------------------------------------------------------------------

\

The following analysis is based on Office Operations questions in the SG19 staff survey,
using only complete responses (n = 1356). The original data has been transformed,
so every staff response (i.e. row) is assgined an Index score between -1 (negative 
responses) and 1 (positive responses). The graphs below show that Index scores for 
questions relating to Office Operations for each Venue/District (Fig A). Overall, 
Office Operations questions scored similarly to other topics - statistical analysis 
shows that the Office Operations Index scores are not significantly different to other 
topics (Fig A). 

\

Within the Office Operations Index scores, all Roles gave mainly positive feedback, 
while Statistical analysis showed that the differences between the Index scores for each 
role were not significant (). Then we can break the Office Operations Index scores down 
by staff demographics, and the geographical remoteness of the Venue/District where staff 
worked (Fig B). Office Operations Index scores did not differ by demographics (), indicating 
the background of SG19 Election Staff did not affect their survey responses (?). Similary, 
the Office Operations Index scores did not differ by geographical remoteness ().

\


### **Fig A). SG19 Survey Responses, aggregated by District across all Topics(left), and by Role for Office (right)**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 15, fig.height = 6}

## Arrange a grid
plot_grid(boxplots_indexes[["bp_district_all"]], 
          boxplots_role_indexes[["bp_district_Role_Office"]],
          nrow = 1,
          label_size = 5, align = 'hv')

```


\

### **Fig B). Office Survey Responses by Demoghraphic (left) and remoteness (right)**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 15, fig.height = 8}

## Arrange a grid
boxplots_combined_facetted_indexes[["bp_district_demography_Office"]]

```

\


### **Fig C). RO Office Survey Responses by geographic remoteness**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 8, fig.height = 5}

## Arrange a grid
boxplots_topic_remoteness_indexes[["Office"]]

```

\



Column {data-width = 1}
-----------------------------------------------------------------------



Index Map
=====================================

\

Column {data-width = 1}
-----------------------------------------------------------------------


Column {data-width = 12}
-----------------------------------------------------------------------

### **Fig B). Office Survey Responses by District**

</br> The map below shows the index of survey reponses for questions relating to Office for the SG19 Staff Survey.
</br> See table of contents for details of how the Index was calculated.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA, fig.align = "center", fig.width = 20, fig.height = 10}

# latticeView(district_satisfaction_choropleth, 
#             district_dissatisfaction_choropleth,
#             
#             ncol = 2,  sync = "none", sync.cursor = FALSE,
#             no.initial.sync = TRUE)

district_Office_choropleth


```



Column {data-width = 1}
-----------------------------------------------------------------------


<!-- Sentiment Analysis -->
<!-- ===================================== -->


<!-- Column {data-width = 1} -->
<!-- ----------------------------------------------------------------------- -->


<!-- Column {data-width = 12} -->
<!-- ----------------------------------------------------------------------- -->


<!-- Column {data-width = 1} -->
<!-- ----------------------------------------------------------------------- -->

