---
title: "IT Questions analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    css: styles_SG19_survey_font.css
---



Index analysis
=====================================

Column {data-width = 1}
-----------------------------------------------------------------------

Column {data-width = 12}
-----------------------------------------------------------------------

\

The following analysis is based on IT questions in the SG19 staff survey,
using only complete responses (n = 1356). The original data has been transformed,
so every staff response (i.e. row) is assgined an Index score between -1 (negative 
responses) and 1 (positive responses). The graphs below show that Index scores for 
questions relating to IT for each Venue/District (Fig A). Overall, IT questions 
scored similarly to other topics - statistical analysis shows that the IT Index 
scores are not significantly different to other topics (Fig A). 

\

Within the IT scores, all Roles gave mainly positive feedback, while Statistical 
analysis showed that the differences between the IT Index scores for each 
role are not significant (). Then we can break the IT Index scores down by staff 
demographics, and the geographical remoteness of the Venue/District where staff worked 
(Fig B). IT Index scores did not differ by demographics (), indicating the background 
of SG19 Election Staff did not affect their survey responses (?). Similary, the IT 
Index scores did not differ by geographical remoteness ().

\


### **Fig A). SG19 Survey Responses, aggregated by District across all Topics (left), and by Role for IT (right)**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 15, fig.height = 6}

## Arrange a grid
plot_grid(boxplots_indexes[["bp_district_all"]], 
          boxplots_role_indexes[["bp_district_Role_IT"]],
          nrow = 1,
          label_size = 5, align = 'hv')

```


\

### **Fig B). IT Survey Responses by Demoghraphic (left) and remoteness (right)**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 15, fig.height = 8}

## Arrange a grid
boxplots_combined_facetted_indexes[["bp_district_demography_IT"]]

```

\


### **Fig C). IT Survey Responses by geographic remoteness**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = "center", fig.width = 8, fig.height = 5}

## Arrange a grid
boxplots_topic_remoteness_indexes[["IT"]]

```

\


Column {data-width = 1}
-----------------------------------------------------------------------


<!-- Sentiment Analysis -->
<!-- ===================================== -->


<!-- Column {data-width = 1} -->
<!-- ----------------------------------------------------------------------- -->


<!-- Column {data-width = 12} -->
<!-- ----------------------------------------------------------------------- -->


<!-- Column {data-width = 1} -->
<!-- ----------------------------------------------------------------------- -->





